Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
update plot value for size 1
comments

\paragraph{Final specification.} The final specification we productized last month takes two or three parameters. The third parameter, the order, is optional. If the third parameter is absent, the VM assumes the byte ordering (ASCII order) is the order to compare against. Therefore, the VM does not need to go through the indirection order array in the common case. The primitive answers a negative value if the first parameter is smaller than the second, 0 if they are equal, and a positive value if the first parameter is greater than the second one.
\cba{Maybe rewrite the last paragraph to make it clearer / more formal. - CF Java spec ?}

@@

@@

    \subcaption{Size 1 TO UPDATE}

@@

    \subcaption{Size 1 TO UPDATE}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

@@

\cba{appendix with full code}

>>>>

\paragraph{Final specification.} The final specification we productized last month takes two or three parameters. The third parameter, the order, is optional. If the third parameter is absent, the VM assumes the byte ordering (ASCII order) is the order to compare against. Therefore, the VM does not need to go through the indirection order array in the common case. The primitive answers a negative value if the first parameter is smaller than the second, 0 if they are equal, and a positive value if the first parameter is greater than the second one.
\cba{Maybe rewrite the last paragraph to make it clearer / more formal. - CF Java spec ? => This is critical, maybe in bold or in a box}

@@

2   0.6013716   0.0023206431 
3   0.5653467   0.007829291
4   1.816869    0.019114984 
5   3.537800    0.012357500 

@@

    \subcaption{Size 1}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        x=0.5cm,
        xtick={1,...,5},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSmartSyntaxPlug, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   0.5605682   0.002198180 
3   0.5566675   0.001023225
4   1.5605275   0.006372279 
5   3.754532    0.01109086 
};            
      \end{axis}
    \end{tikzpicture}

    \subcaption{Size 1}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

@@

\cba{I think in the fig we should also see the ASM cog generate}
